The Gamma: Programmatic Data Exploration for Non-programmers

### 2022-06-10 wip-design/paper.tex
Edits, VL/HCC version

\begin{document}
\title{Iterative Prompting: Programmatic Data Exploration for Non-programmers}

@@

\begin{abstract}
  Data exploration tools based on code have many desirable characteristics. They can easily access
  a wide range of different data sources, result in reproducible scripts and encourage users to
  reuse and modify existing code. Unfortunately, most programming tools require expert
  coding skills. Can we make data exploration based on code accessible to non-experts?
  %
  We present The Gamma, a novel text-based data exploration environment that answers the question in
  the affirmative. The Gamma is based on a novel interaction principle, \emph{iterative prompting},
  which lets users create transparent and reproducible scripts without writing code. The Gamma lowers
  the barrier to entry and learning from previously created data analyses. We evaluate the usability
  of The Gamma through a user study on non-technical employees of a research institute.
  %
  Our work shows that we may not need to shy away from code in order to build accessible,
  reproducible and transparent tools that will allow a broad audience to benefit from the
  rise of open data.
\end{abstract}

>>>>

\begin{document}
\title{The Gamma: Programmatic Data Exploration for Non-programmers}

@@

\begin{abstract}
Data exploration tools based on code have many desirable characteristics. They can easily access
a wide range of different data sources, result in reproducible scripts and encourage users to
reuse and modify existing code. Unfortunately, most programming tools require expert
coding skills. Can we make data exploration based on code accessible to non-experts?

We present The Gamma, a novel text-based data exploration environment that answers the question in
the affirmative. The Gamma is takes the code completion mechanism to the limit.
By repeatedly choosing from offered completions, users can create transparent and reproducible
scripts without writing code. We evaluate the usability of The Gamma through a user
study on non-technical employees of a research institute.

Our work shows that we may not need to shy away from code in order to build accessible,
reproducible and transparent tools that will allow a broad audience to benefit from the
rise of open data.
\end{abstract}
